Library of Actions: Implementing Human-like Manipulation Actions based on Semantic Event Chains

### 2014-05-20 paper_new.tex
tex file cleaned up

% In this paper a novel structure 
% the library of action is introduced which is an application software developed in Orocos framework.
\keywords{library of actions \and manipulation actions \and semantic event chains \and }
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% It remains largely a puzzle how action knowledge can be efficiently structured for robotics applications.
% In a recent paper \cite{TAMD13}, we had discussed that human manipulation actions can be captured by a limited ontology-tree
% and we had argued that there is only a quite small number of basic actions existing (less than 30), which cover most if not all of our uni-manual manipulations.
% 
% This, we believe, offers the unique opportunity to structure the robot's manipulation action-space
% by defining all these actions in a default way to also store them in an action library.
% For any given robot (with not too different embodiment) execution of an action then means to access the required library function
% only having to re-parameterize it with respect to the {\em specific} action-situation (the scene) also taking into account all embodiment-specific constraints.
% 
% This idea as such is quite straight-forward but requires addressing many difficult problems.
% First and foremost we are asking for an appropriate action-representation from which an action library could be formed.
% Second, we need to define an architecture that can be used to access the library and actually execute an action.
% % \begin{figure}
% % % Use the relevant command to insert your figure file.
% % % For example, with the graphicx package use
% %   \includegraphics{example.eps}
% % % figure caption is below the figure
% % \caption{Please write your figure caption here}
% % \label{fig:1}       % Give a unique label
% % \end{figure}
\begin{figure}
      \centering
      \includegraphics[scale=0.6]{./pdf/overview.pdf}
      \caption{An action is defined and executed using three levels.}
      \label{fig:overview}
\end{figure}

@@

A simple action like putting a bucket on a box may be described by a human as following:
\begin{enumerate}
  \item \textbf{\textit{Approach}} the bucket
  \item \textbf{\textit{Grasp}} the bucket
  \item \textbf{\textit{Put}} the bucket on the box
  \item \textbf{\textit{Release}} the bucket
\end{enumerate}
This description is by no means unique.
One could easily describe the same action in different words, with different number of steps and different details.
% However, there are a few points that we can use from this simple example:
However, one could still extract some properties from this simple description:
\begin{itemize}
  \item \textbf{Property 1:} The definition is valid even if the objects are changed.
  \item \textbf{Property 2:} An action can be broken into a sequence of smaller sub-actions such as \textit{approach} and \textit{grasp}.
  \item \textbf{Property 3:} There are conditions to end one sub-action and start the next. In the above example these conditions are rather implicit.
  \item \textbf{Property 4:} As humans, we roughly know how to perform these sub-actions.
  Although, our exact movements are produced when we see the objects and perform the action.
\end{itemize}

@@

% Throughout this paper we will develop the \textit{put-on-top} example to demonstrate our approach.

% In this section, a symbolic high-level definition of actions is presented.
This high-level symbolic definition has several components which will be described in the rest of this section.
For the put-on-top example, the resulting components are shown in fig.\ref{fig:action_graph_sec}.
This definition is an extension to our previous works on the ontology of actions \cite{TAMD13}, semantic event chains (SEC) \cite{Aksoy11b},
and first version of our action library \cite{aein2013toward}.
\begin{figure*}
      \centering
      \includegraphics[scale=0.20]{./pdf/action_graph_sec_new2.pdf}
      \caption{ An example of the put-on-top action is performed by a human. 
The snapshots of the executed actions together with segmented images are shown (top).
The symbolic graph sequence (middle) and the SEC matrix (bottom) together with 
the required primitives (bottom right) give a high-level definition of the action.
The abstract objects, manipulator, primary object, secondary object and background are the hand, the bucket, the box and the table, respectively.}
      \label{fig:action_graph_sec}
\end{figure*}
% First we give a short description of the ontology of actions.
% Then, the symbolic components of actions are introduced.
% The components of this level are as follows:
% Text with citations \cite{RefB} and \cite{RefJ}
% citations \cite{Aein12} and \cite{Aksoy11b}.
\subsection{Ontology of Actions}
\label{sec:ontology}
The \textit{ontology of manipulation actions} \cite{TAMD13} defines human-like manipulation actions in an abstract way.
An action is defined as change of touching relations between pairs of objects.
The hypothesis is that the most important information are encoded in touching relation of objects.
% Such definition of action is depicted in fig.xxx.
An example put-on-top actions which is performed by human is shown in fig.\ref{fig:action_graph_sec}.
The segmented images and the extracted graph sequence are also shown.
The nodes of the graphs represent objects and presence of an edge indicates that a pair of objects are touching.
The full action is thus summarized by this sequence of graphs.

@@

Therefore the last object that we add to the action definition is the \textit{background}.
In our example, the background is the table.
The result is that the number of objects involved in an action is (at most) four: manipulator, primary object, secondary object and background.
% For the put-on example depicted in Fig. \ref{fig:action_graph_sec}, these objects are tool=hand, obj1=box, obj2=box and background=table.

% When these abstract objects are instantiated in the real world, they are represented by one point in Cartesian space located at their center of mass.
% For some actions and objects, however, more that just a single point is needed.
% For example, to cut an object like a banana, we need to know the angle that it makes with the X-axis, to adjust the angle of knife.
% In this case we use models to describe objects.
% In the cutting example, we use a line model which has a parameter that shows the angle of banana.
\begin{table}
% \centering
\caption{Abstract relations and their attributes for the put-on-top action}
\begin{tabular}{ lllll }
% \caption{}
\hline\noalign{\smallskip}
Relation Name & Abstract Relation & Real Relation & Type \\
\noalign{\smallskip}\hline\noalign{\smallskip}
$\text{R}_1$  & R(manipulator,primary object) & R(hand,bucket) & variable \\
% \hline
$\text{R}_2$  & R(manipulator,secondary object)& R(hand,box) & don't-care \\
% \hline
$\text{R}_3$  & R(manipulator,background) & R(hand,table) & don't-care \\
% \hline
$\text{R}_4$  & R(primary object,secondary object) & R(bucket,box) & variable  \\
% \hline
$\text{R}_5$  & R(primary object,background) & R(bucket,table) & variable \\
% \hline
$\text{R}_6$  & R(secondary object,background)& R(box,table) & constant \\
\noalign{\smallskip}\hline
\end{tabular}
% \caption{Abstract relations and their attributes for the put-on action}
\label{tab:relations}
\end{table}

@@

The \emph{value} of a relation is either N (for Not touching), T (for Touching) or A (for absent).
Absent value happens when there is no information about the relation, e.g., one object is not defined or not visible.
Table \ref{tab:relations} shows the abstract relations and their type attributes for the put-on-top action.
% The \emph{sensor} attribute of a relation, determines the type of sensor that is used to detect that relation.
% We use position, tactile, force and vision sensors to obtain the value of a relation.

@@

%  the relation between a pair of objects.
% The symbolic entries show the semantic relation between the corresponding pair.
The valid symbolic entries of SEC matrix are N (not touching), T (touching) and A ( absence).
In a SEC, the progress of the action from the beginning to the end, is seen in a compact way.
In addition, the SEC matrix of different instances of one action remains the same.
The SEC matrix of the put-on-top action is shown in Fig.\ref{fig:action_graph_sec}.
% \begin{figure*}
%       \centering
%       \includegraphics[scale=0.2]{./pdf/action_graph_sec.pdf}
%       \caption{ The relation of 
% Two put-on actions are done with different objects and positions.
% The snapshots of real action execution together with graphs annotated to objects are depicted at top.
% The symbolic graphs 
% However, the SEC matrix and graph sequences are the same.}
%       \label{fig:action_graph_sec}
% \end{figure*}

\subsection{Abstract Primitives}
\label{sec:abstract_primitives}
In the simple example at the beginning of this section, it is shown that a full action can be divided into several sub-actions.
These sub-actions or \textit{primitives} are the basic functions of the manipulator.
% One example is the ability of a human or robot arm to move to a certain pose.

% The proper combination of these primitives form actions 
% While these primitives are necessary to perform actions, they alone don't form a full purposeful actions.
% What forms an action, is the proper combination of them.
In our approach we define the following primitives:
\begin{itemize}
 \item $move(pose)$ :  The manipulator moves to $pose$.
 \item $move_{periodic}(path)$ : The robot arm moves periodically along the given path.
 \item $force()$ : The robot arm exerts $force$.
 \item $grasp()$ : The robot hand grasps an object.
 \item $release()$ : The robot hand releases an object.
\end{itemize}

@@

As described above, one important primitive is the $move(pose)$ primitive that moves the robot arm toward a pose.
In the abstract definition, the argument $pose$ of this primitive is an abstract position.
The abstract positions are either the objects in the scene, or some other convenient points in space.
% The target of the $move$ primitive is either an object in the scene, or just a point in space.
While performing the actions, sometimes we move our hands toward points in space where there are no specific objects.
One example is when we initially lift an object from a table, to put it on top of another object.
We move the object to a point that makes our next move easier.
We call such positions \textit{home}.

In some actions, we need to move toward arbitrary positions to achieve the goal of the action.
For example in the pushing action, we push an object to a desired position.
This desired position could be any accessible point and it is usually specified by the user or a higher level planner.
We call this type of abstract positions the \textit{goal} position.
% We call such points, abstract positions, and use them in our method.
% 
% In our method, we use two kinds of abstract positions, namely \emph{home} and \emph{goal} positions.
% The example above was a home position, while an example of a goal position is when we push an object on a surface to another point.
% The actual definition of abstract positions depends on the action and position of other objects.
% In Fig. \ref{fig:action_graph_sec} it is shown that the primitive $move(home)$ is used twice in this action.
% \subsection{Complete Definition}
% In the previous sub-sections several components of the high-level definition were introduced.
% Here we sum up the high-level definition with the same example that we started this section with.
% In figure.xx , an example of a put on top action is depicted.
% The snapshots shows the different states of the scene in terms of object relations.
% The corresponding SEC matrix as well as the required primitives to move from one state to the next state are shown.
% % The whole actions is transformed into a finite state machine which shows the states, and the associated primitives.
% 
% This definition is general and abstract,
% however, one needs to relate these symbols with the real world, which is done in the next section.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Low-level Action Definition}
\label{sec:low-level}
In this section, the abstract components of the high-level definition are related to their real-world counterparts.
This includes defining objects in the real world, implementing the low-level primitives such that proper commands are sent to the hardware control systems,
and calculating the object relations from the sensor data.
In the rest of this section, these steps are described in more detail.

@@

\begin{table}
% \centering
\caption{Summary of object relation detection in different actions. For each relation only the main sensor is mentioned.}
\begin{tabular}{ lcccccc }
% \caption{}
\hline\noalign{\smallskip}
 Action Name &  $\text{R}_1$ & $\text{R}_2$ &$\text{R}_3$ &$\text{R}_4$ &$\text{R}_5$&$\text{R}_6$ \\
\noalign{\smallskip}\hline\noalign{\smallskip}
 Pick and Place & tactile & -       & position & -     &  force & - \\
 Put-on-top     & tactile & tactile & position & force &  vision & vision \\
 Take-down      & tactile & tactile & position & vision&  force & vision \\
 Put-in         & tactile & tactile & position & force &  vision & vision \\
 Cut            & tactile & tactile & position & force &  position & vision \\
 Unload         & tactile & tactile & position & vision&  force & vision \\
 Stir           & tactile & -       & position & vision&  vision & - \\
 Push           & force   & -       & position & -     &  vision & - \\
 Poke           & force   & -       & position & -     &  vision & - \\
\noalign{\smallskip}\hline
\end{tabular}
% \caption{Abstract relations and their attributes for the put-on action}
\label{tab:relation_detection}
\end{table}
\subsection{Real relations}
\label{sec:real_relations}
The real relations are the actual relations between pairs of objects.
These relations together form a symbolic representation of the scene, or in other words, the current state of system.
To detect the relations, we use combination of vision, position, force and tactile sensors.

@@

% This can be calculated simply by comparing the position of robot hand and the height of the background (assuming that we have a flat background).

@@

% \begin{table}
% % \centering
% \caption{Summary of object relation detection by different sensors}
% \begin{tabular}{ lllll }
% % \caption{}
% \hline\noalign{\smallskip}
% \# & Abstract Relation &  Before/After Action& During Action\\
% \noalign{\smallskip}\hline\noalign{\smallskip}
% $1$  & R(manipulator,primary obj.) & vison, tactile& position, tactile, vision \\
% % \hline
% $2$  & R(manipulator,secondary obj.)& vison, tactile& position, tactile, vision \\
% % \hline
% $3$  & R(manipulator,background) &  vision,position &  position, vision\\
% % \hline
% $4$  & R(primary obj.,secondary obj.) & vision &  position, force, vision\\
% % \hline
% $5$  & R(primary obj.,background) & vision &  position, force, vision\\
% % \hline
% $6$  & R(secondary obj.,background) & vision &  vision\\
% \noalign{\smallskip}\hline
% \end{tabular}
% % \caption{Abstract relations and their attributes for the put-on action}
% \label{tab:relation_detection}
% \end{table}

@@

The $exert(f_{des},P)$ performs force control with set-point $f_{des}$.
In our setup, we use a parallel force/position scheme with dominant force control, similar to \cite{chiaverini1993parallel}.
In this way we can achieve the desired force in the constrained space, and at the same time, perform desired motions in the unconstrained space,
the trajectory of which is defined by $P$.
% For example in cutting action, the robot arm keeps a constant force between the knife and banana in Z direction (constrained space),
% while moving the knife back and forth in the XY-plane (unconstrained space).

@@

% \begin{figure}[t]
%       \centering
%       \includegraphics[scale=0.28]{./pdf/sec_fsm.pdf}
%       \caption{A mid-level sequencer is implemented by a finite state machine (FSM) for the put-on-top action.
% The action starts if initially inputs (real relations) match the first column of the SEC matrix.
% The transition from state $i$ to $i+1$ occurs when the inputs match the $i$-th column of the SEC matrix.
% Otherwise, the next state is the same as the current state (loop transitions).
% This process is continued until reaching the final state which corresponds to the last column of the SEC matrix.
% }
%       \label{fig:sec_fsm}
% \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementing the Actions}
\label{sec:Implementing}

In this section we present our implementation of manipulation actions based on the high-level and low-level definitions given in the previous sections.
First we introduce the hardware setup used in the experiments.
Then, we present the software components that are developed as part of the library of actions.
Finally, our algorithm for executing actions is described as a finite state machine.
% At the end of this section, we show the specific hardware setup that we used to produce our results.

@@

\subsection{Software}
\label{sec:software}
The library of actions is implemented as an application in the Open Robot Control Software (Orocos) framework \cite{rtt-url,soetens2006}.
The Orocos is a framework to develop real-time robotic and automation applications.
In a typical Orocos application, several components exist which communicate over (possibly real-time) data ports.
The library of actions consists of several components which are shown in fig.\ref{fig:aladdin_structure}.
Some of the components communicate to hardware (Sensors and actuators), while others perform calculations and control the execution of actions.
The components are described in the following:
% \subsection{Hardware-related Components}
\begin{figure*}
      \centering
      \includegraphics[scale=1]{./pdf/aladdin_structure_new.pdf}
      \caption{ Block diagram of the software for action library.
      The interconnection of the components are shown as well as the interface to ROS nodes and hardware.
}
      \label{fig:aladdin_structure}
\end{figure*}
% There hardware-related components are the following:

% \subsection{Calculation and Control Components}

% The components which are used for action definition and execution are 
\begin{itemize}
 \item{\textbf{Action}}
component holds the parameters of the high-level definition of the action.
These parameters are the SEC matrix, high-level primitives and the abstract arguments.
The parameters of the DMP for trajectories are also stored in this component.
\item{\textbf{Perception}}
component collects data from all the sensors and determines if the relations of objects in the scene are altered.
It receives the object poses from the vision system (through the ROS-interface component).
It also monitors other sensors and detects changes in object relations according to section.\ref{sec:real_relations}.
\item{\textbf{Coordinator}}
component contains a state machine that executes the action.
The detail of the state machine and execution algorithm will be discussed in \ref{sec:execution_algorithm}.
Additionally, some function like comparing desired and actual relations is done inside this component.

\item{\textbf{Trajectory Generator}}
component receives $move()$ and $move_{periodic}()$ primitives and generates the trajectory using the DMPs.
% It is created by modifying the CartesianGeneratorPos component in \textit{cartesian\_motion\_control} package (reference needed).
% The DMP implementation is according to \cite{Kulvicius2012}.

@@

\item{\textbf{ROS interface}}
% Our vision system communicates over ROS nodes.
component creates an interface between the ROS nodes and Orocos data ports.
The data ports in Orocos are capable of talking to ROS nodes, using the components of $rtt\_ros\_integration$ stack.
% \footnote{http://wiki.ros.org/rtt_ros_integration}.
This component is created using the $rtt\_rosnode$ component of this stack to integrate all ROS communications in one component.
Since our vision system is developed in ROS framework, this component is used to get the information such as 
objects poses and relations from the vision system and create the necessary data ports to send them to other components.
\end{itemize}

% \paragraph{Action}
% The action component holds the parameters of the high-level definition of the action.
% These parameters are the SEC matrix, high-level primitives and the abstract arguments.
% The parameters of the DMP for trajectories are also stored in this component.
% \paragraph{Perception}
% The perception component collects data from all the sensors and determines if relation of objects in the scene are modified.
% It receives the object poses from the vision system (through the ROS-interface component).
% It also monitors other sensors and detects changes in object relations according to section.\ref{sec:real_relations}.
% \paragraph{Coordinator}
% The coordinator component contains a state machine that executes the action.
% The detail of the state machine and execution algorithm will be discussed in \ref{sec:execution_algorithm}.
% Additionally, some function like comparing desired and actual relations is done inside this component.
% 
% \paragraph{Trajectory planner}
% The trajectory planner receives $move()$ and $move_{periodic}()$ primitives and generates the trajectory using the DMPs.
% % It is created by modifying the CartesianGeneratorPos component in \textit{cartesian\_motion\_control} package (reference needed).
% % The DMP implementation is according to \cite{Kulvicius2012}.
% 
% \paragraph{Force Control}
% The force control component implements the $exert()$ primitive.
% The actual contact force is received from the FRI component and using the algorithm of section.\ref{section_primitives},
% the contact force is regulated in the desired direction.
% The output of this component is sent to the control system of the LWR arm, though the FRI component.
% 
% \paragraph{FRI Component}
% The FRI Component communicates with the robot arm through the FRI,
% and provides the necessary input and output data ports to other Orocos components.
% 
% \paragraph{SDH Component}
% The hand primitives (grasp, release and pre-shape) are implemented in this component.
% This component uses the C++ library which is provided to communicate with the Schunk SDH-2 robot hand.
% The tactile sensor data are also processed in this component to detect objects in the hand.
% The parameter $hand\_status$ determines the current status of the hand and is sent to the perception component.
% This parameter takes values : Undefined, Grasped and Empty
% 
% \paragraph{ROS interface}
% % Our vision system communicates over ROS nodes.
% The data ports in Orocos are capable of talking to ROS nodes, using the components of $rtt\_ros\_integration$ stack.
% % \footnote{http://wiki.ros.org/rtt_ros_integration}.
% The ROS interface component is created by using $rtt\_rosnode$ component of this stack to integrate all ROS communications in one component.
% Since our vision system is developed in ROS framework, this component is used to get the information such as 
% objects poses and relations from the vision system and create the necessary data ports to send them to other components.

\subsection{Execution Algorithm}
\label{sec:execution_algorithm}
\begin{figure*}
      \centering
      \includegraphics[scale=1]{./pdf/coordinator_fsm2.pdf}
      \caption{ State diagram of the finite state machine governing the execution of action.
}
      \label{fig:coordinator_fsm}
\end{figure*}
Here an algorithm is presented to execute actions, using the software components introduced earlier.
The core of the execution is a finite state machine inside the coordinator component.
% This component receives the object relations from the perception component and decides which primitive should be executed by hardware.
% To do this, it receives the high-level action definition from the action component.

@@

% A state machine has an initial state, a final state and optionally some other states.
% A state machine is at any time in exactly one of its states.
% Each state has entry, run and exit functions that are called when that state is entered, running and left, respectively.

% The state machine which is used here is conceptually similar to the mid-level sequencer which is used in \cite{aein2013toward}.

>>>>

\keywords{library of actions \and manipulation actions \and semantic event chains \and }
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% It remains largely a puzzle how action knowledge can be efficiently structured for robotics applications.
% In a recent paper \cite{TAMD13}, we had discussed that human manipulation actions can be captured by a limited ontology-tree
% and we had argued that there is only a quite small number of basic actions existing (less than 30), which cover most if not all of our uni-manual manipulations.
% 
% This, we believe, offers the unique opportunity to structure the robot's manipulation action-space
% by defining all these actions in a default way to also store them in an action library.
% For any given robot (with not too different embodiment) execution of an action then means to access the required library function
% only having to re-parameterize it with respect to the {\em specific} action-situation (the scene) also taking into account all embodiment-specific constraints.
% 
% This idea as such is quite straight-forward but requires addressing many difficult problems.
% First and foremost we are asking for an appropriate action-representation from which an action library could be formed.
% Second, we need to define an architecture that can be used to access the library and actually execute an action.
% % \begin{figure}
% % % Use the relevant command to insert your figure file.
% % % For example, with the graphicx package use
% %   \includegraphics{example.eps}
% % % figure caption is below the figure
% % \caption{Please write your figure caption here}
% % \label{fig:1}       % Give a unique label
% % \end{figure}
% \begin{figure}
%       \centering
%       \includegraphics[scale=0.6]{./pdf/overview.pdf}
%       \caption{An action is defined and executed using three levels.}
%       \label{fig:overview}
% \end{figure}

@@

A simple action like putting a bucket on a box may be described by a human as following:
\begin{enumerate}
  \item \textbf{\textit{Approach}} the bucket
  \item \textbf{\textit{Grasp}} the bucket
  \item \textbf{\textit{Put}} the bucket on the box
  \item \textbf{\textit{Release}} the bucket
\end{enumerate}
This description is by no means unique.
One could easily describe the same action in different words, with different number of steps and different details.
However, one could still extract some properties from this simple description:
\begin{itemize}
  \item \textbf{Property 1:} The definition is valid even if the objects are changed.
  \item \textbf{Property 2:} An action can be broken into a sequence of smaller sub-actions such as \textit{approach} and \textit{grasp}.
  \item \textbf{Property 3:} There are conditions to end one sub-action and start the next. In the above example these conditions are rather implicit.
  \item \textbf{Property 4:} As humans, we roughly know how to perform these sub-actions.
  Although, our exact movements are produced when we see the objects and perform the action.
\end{itemize}

@@

This high-level symbolic definition has several components which will be described in the rest of this section.
For the put-on-top example, the resulting components are shown in fig.\ref{fig:action_graph_sec}.
This definition is an extension to our previous works on the ontology of actions \cite{TAMD13}, semantic event chains (SEC) \cite{Aksoy11b},
and first version of our action library \cite{aein2013toward}.
\begin{figure*}
      \centering
      \includegraphics[scale=0.20]{./pdf/action_graph_sec.pdf}
      \caption{ An example of the put-on-top action is performed by a human. 
The snapshots of the executed actions together with segmented images are shown (top).
The symbolic graph sequence (middle) and the SEC matrix (bottom) together with 
the required primitives (bottom right) give a high-level definition of the action.
The abstract objects, manipulator, primary object, secondary object and background are the hand, the bucket, the box and the table, respectively.}
      \label{fig:action_graph_sec}
\end{figure*}

\subsection{Ontology of Actions}
\label{sec:ontology}
The \textit{ontology of manipulation actions} \cite{TAMD13} defines human-like manipulation actions in an abstract way.
An action is defined as change of touching relations between pairs of objects.
The hypothesis is that the most important information are encoded in touching relation of objects.
An example put-on-top actions which is performed by human is shown in fig.\ref{fig:action_graph_sec}.
The segmented images and the extracted graph sequence are also shown.
The nodes of the graphs represent objects and presence of an edge indicates that a pair of objects are touching.
The full action is thus summarized by this sequence of graphs.

@@

Therefore the last object that we add to the action definition is the \textit{background}.
In our example, the background is the table.
The result is that the number of objects involved in an action is (at most) four: manipulator, primary object, secondary object and background.

\begin{table}
\caption{Abstract relations and their attributes for the put-on-top action}
\begin{tabular}{ lllll }
\hline\noalign{\smallskip}
Relation Name & Abstract Relation & Real Relation & Type \\
\noalign{\smallskip}\hline\noalign{\smallskip}
$\text{R}_1$  & R(manipulator,primary object) & R(hand,bucket) & variable \\
$\text{R}_2$  & R(manipulator,secondary object)& R(hand,box) & don't-care \\
$\text{R}_3$  & R(manipulator,background) & R(hand,table) & don't-care \\
$\text{R}_4$  & R(primary object,secondary object) & R(bucket,box) & variable  \\
$\text{R}_5$  & R(primary object,background) & R(bucket,table) & variable \\
$\text{R}_6$  & R(secondary object,background)& R(box,table) & constant \\
\noalign{\smallskip}\hline
\end{tabular}
\label{tab:relations}
\end{table}

@@

The \emph{value} of a relation is either N (for Not touching), T (for Touching) or A (for absent).
Absent value happens when there is no information about the relation, e.g., one object is not defined or not visible.
Table \ref{tab:relations} shows the abstract relations and their type attributes for the put-on-top action.

@@

The valid symbolic entries of SEC matrix are N (not touching), T (touching) and A ( absence).
In a SEC, the progress of the action from the beginning to the end, is seen in a compact way.
In addition, the SEC matrix of different instances of one action remains the same.
The SEC matrix of the put-on-top action is shown in Fig.\ref{fig:action_graph_sec}.

\subsection{Abstract Primitives}
\label{sec:abstract_primitives}
In the simple example at the beginning of this section, it is shown that a full action can be divided into several sub-actions.
These sub-actions or \textit{primitives} are the basic functions of the manipulator.

In our approach we define the following primitives:
\begin{itemize}
 \item $move(pose)$ :  The manipulator moves to $pose$.
 \item $move_{periodic}(path)$ : The robot arm moves periodically along the given path.
 \item $force()$ : The robot arm exerts $force$.
 \item $grasp()$ : The robot hand grasps an object.
 \item $release()$ : The robot hand releases an object.
\end{itemize}

@@

As described above, one important primitive is the $move(pose)$ primitive that moves the robot arm toward a pose.
In the abstract definition, the argument $pose$ of this primitive is an abstract position.
The abstract positions are either the objects in the scene, or some other convenient points in space.
While performing the actions, sometimes we move our hands toward points in space where there are no specific objects.
One example is when we initially lift an object from a table, to put it on top of another object.
We move the object to a point that makes our next move easier.
We call such positions \textit{home}.

In some actions, we need to move toward arbitrary positions to achieve the goal of the action.
For example in the pushing action, we push an object to a desired position.
This desired position could be any accessible point and it is usually specified by the user or a higher level planner.
We call this type of abstract positions the \textit{goal} position.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Low-level Action Definition}
\label{sec:low-level}
In this section, the abstract components of the high-level definition are related to their real-world counterparts.
This includes defining objects in the real world, implementing the low-level primitives such that proper commands are sent to the hardware control systems,
and calculating the object relations from the sensor data.
In the rest of this section, these steps are described in more detail.

@@

\begin{table}
\caption{Summary of object relation detection in different actions. For each relation only the main sensor is mentioned.}
\begin{tabular}{ lcccccc }
\hline\noalign{\smallskip}
 Action Name &  $\text{R}_1$ & $\text{R}_2$ &$\text{R}_3$ &$\text{R}_4$ &$\text{R}_5$&$\text{R}_6$ \\
\noalign{\smallskip}\hline\noalign{\smallskip}
 Pick and Place & tactile & -       & position & -     &  force & - \\
 Put-on-top     & tactile & tactile & position & force &  vision & vision \\
 Take-down      & tactile & tactile & position & vision&  force & vision \\
 Put-in         & tactile & tactile & position & force &  vision & vision \\
 Cut            & tactile & tactile & position & force &  position & vision \\
 Unload         & tactile & tactile & position & vision&  force & vision \\
 Stir           & tactile & -       & position & vision&  vision & - \\
 Push           & force   & -       & position & -     &  vision & - \\
 Poke           & force   & -       & position & -     &  vision & - \\
\noalign{\smallskip}\hline
\end{tabular}
\label{tab:relation_detection}
\end{table}
\subsection{Real relations}
\label{sec:real_relations}
The real relations are the actual relations between pairs of objects.
These relations together form a symbolic representation of the scene, or in other words, the current state of system.
To detect the relations, we use combination of vision, position, force and tactile sensors.

@@

@@

@@

The $exert(f_{des},P)$ performs force control with set-point $f_{des}$.
In our setup, we use a parallel force/position scheme with dominant force control, similar to \cite{chiaverini1993parallel}.
In this way we can achieve the desired force in the constrained space, and at the same time, perform desired motions in the unconstrained space,
the trajectory of which is defined by $P$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementing the Actions}
\label{sec:Implementing}

In this section we present our implementation of manipulation actions based on the high-level and low-level definitions given in the previous sections.
First we introduce the hardware setup used in the experiments.
Then, we present the software components that are developed as part of the library of actions.
Finally, our algorithm for executing actions is described as a finite state machine.

@@

\subsection{Software}
\label{sec:software}
The library of actions is implemented as an application in the Open Robot Control Software (Orocos) framework \cite{rtt-url,soetens2006}.
The Orocos is a framework to develop real-time robotic and automation applications.
In a typical Orocos application, several components exist which communicate over (possibly real-time) data ports.
The library of actions consists of several components which are shown in fig.\ref{fig:aladdin_structure}.
Some of the components communicate to hardware (Sensors and actuators), while others perform calculations and control the execution of actions.
The components are described in the following:
\begin{figure*}
      \centering
      \includegraphics[scale=1]{./pdf/aladdin_structure.pdf}
      \caption{ Block diagram of the software for action library.
      The interconnection of the components are shown as well as the interface to ROS nodes and hardware.
}
      \label{fig:aladdin_structure}
\end{figure*}

\begin{itemize}
 \item{\textbf{Action}}
component holds the parameters of the high-level definition of the action.
These parameters are the SEC matrix, high-level primitives and the abstract arguments.
The parameters of the DMP for trajectories are also stored in this component.
\item{\textbf{Perception}}
component collects data from all the sensors and determines if the relations of objects in the scene are altered.
It receives the object poses from the vision system (through the ROS-interface component).
It also monitors other sensors and detects changes in object relations according to section.\ref{sec:real_relations}.
\item{\textbf{Coordinator}}
component contains a state machine that executes the action.
The detail of the state machine and execution algorithm will be discussed in \ref{sec:execution_algorithm}.
Additionally, some function like comparing desired and actual relations is done inside this component.

\item{\textbf{Trajectory Generator}}
component receives $move()$ and $move_{periodic}()$ primitives and generates the trajectory using the DMPs.

@@

\item{\textbf{ROS interface}}
component creates an interface between the ROS nodes and Orocos data ports.
The data ports in Orocos are capable of talking to ROS nodes, using the components of $rtt\_ros\_integration$ stack.
% \footnote{http://wiki.ros.org/rtt_ros_integration}.
This component is created using the $rtt\_rosnode$ component of this stack to integrate all ROS communications in one component.
Since our vision system is developed in ROS framework, this component is used to get the information such as 
objects poses and relations from the vision system and create the necessary data ports to send them to other components.
\end{itemize}

\subsection{Execution Algorithm}
\label{sec:execution_algorithm}
\begin{figure*}
      \centering
      \includegraphics[scale=1]{./pdf/coordinator_fsm.pdf}
      \caption{ State diagram of the finite state machine governing the execution of action.
}
      \label{fig:coordinator_fsm}
\end{figure*}
Here an algorithm is presented to execute actions, using the software components introduced earlier.
The core of the execution is a finite state machine inside the coordinator component.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
      \centering
      \includegraphics[scale=0.20]{./pdf/result_puton.pdf}
      \caption{ Two instances of the put-on-top action, performed by our method, are shown with different objects and positions. 
The snapshots of the executed actions together with segmented images are shown (top) which indicate the real objects and relations.
The symbolic graph sequence (middle) and the SEC matrix (bottom) remain the same for both version.
}
      \label{fig:result_puton}
\end{figure*}
\section{Results}
\label{sec:results}
